Enabling conditions for effective community based marine reserves in small scale fisheries

### 2018-02-27 Frontiers_Manuscript/Villasenor-Derbez.Rmd
Added xaringan presentation

```{r load_spatial}

# Determine a projection for the maps
proj <- CRS("+proj=longlat +datum=NAD27")

@@

L_catches <- ggplot(L_conapesca, aes(x = Ano, y = PesoVivo/1000, color = Comunidad, group = Comunidad, fill = Comunidad)) +
  geom_smooth(method = "lm") +
  geom_point(aes(shape = Comunidad), size = 2, alpha = 0.5) +
  scale_color_brewer(palette = "Set1") +
  geom_vline(xintercept = c(2006, 2012, 2013), color = c("red", "blue", "darkgreen"), linetype = "dashed", size = 0.5) +
  labs(x = "Year", y = "Catches (Tones)") +
  theme(legend.position = "none",
        text = element_text(size = 12))

L_value <- ggplot(L_conapesca, aes(x = Ano, y = Valor/1e6, color = Comunidad, group = Comunidad, fill = Comunidad)) +
  geom_smooth(method = "lm") +
  geom_point(aes(shape = Comunidad), size = 2, alpha = 0.5) +
  scale_color_brewer(palette = "Set1") +
  geom_vline(xintercept = c(2006, 2012, 2013), color = c("red", "blue", "darkgreen"), linetype = "dashed", size = 0.5) +
  labs(x = "Year", y = "Value (M MXP)") +
  theme(legend.position = "none",
        text = element_text(size = 12))

>>>>

```{r load_spatial}
# Determine a projection for the maps
proj <- CRS("+proj=longlat +datum=NAD27")

@@

L_catches <- ggplot(L_conapesca, aes(x = Ano, y = PesoVivo/1000, color = Comunidad, group = Comunidad, fill = Comunidad)) +
  geom_smooth(method = "lm") +
  geom_point(aes(shape = Comunidad), size = 2, alpha = 0.5) +
  scale_color_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  geom_vline(xintercept = c(2006, 2012, 2013), color = c("red", "blue", "darkgreen"), linetype = "dashed", size = 0.5) +
  labs(x = "Year", y = "Catches (Tones)") +
  theme(legend.position = "none",
        text = element_text(size = 12))

L_value <- ggplot(L_conapesca, aes(x = Ano, y = Valor/1e6, color = Comunidad, group = Comunidad, fill = Comunidad)) +
  geom_smooth(method = "lm") +
  geom_point(aes(shape = Comunidad), size = 2, alpha = 0.5) +
  scale_color_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  geom_vline(xintercept = c(2006, 2012, 2013), color = c("red", "blue", "darkgreen"), linetype = "dashed", size = 0.5) +
  labs(x = "Year", y = "Value (M MXP)") +
  theme(legend.position = "none",
        text = element_text(size = 12))
